데이터 과학을 위한 저작도구: Computational Documents

### 2020-12-04 publisher-journal-api.Rmd
added orcid
start crossref

---
layout: page
title: "데이터 과학을 위한 저작도구: Computational Documents"
subtitle: "출판사, 저널, 논문 API"
author:
- name: "이광춘"
  url: "[Tidyverse Korea](https://www.facebook.com/groups/tidyverse/)"
date: "`r Sys.Date()`"
output:
  html_document: 
    include:
      after_body: footer.html
      before_body: header.html
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
bibliography: bibliography-cd.bib
csl: biomed-central.csl
urlcolor: blue
linkcolor: blue
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
layout: page
title: "데이터 과학을 위한 저작도구: Computational Documents"
subtitle: "출판사, 저널, 논문 API"
author:
- name: "이광춘"
  affiliation: "[Tidyverse Korea](https://www.facebook.com/groups/tidyverse/)"
date: "`r Sys.Date()`"
tags: ["데이터 사이언스", "데이터 과학", "data science", "cross reference", "tidyverse"]
output:
  html_document: 
    include:
      after_body: footer.html
      before_body: header.html
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
bibliography: bibliography-cd.bib
csl: biomed-central.csl
urlcolor: blue
linkcolor: blue
editor_options: 
  chunk_output_type: console
---

@@

![](fig/overview-orcid.png)
